---
title: "Trial & Error"
author: "columbaspexit"
date: "4/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Two things going on here.  

  1. (trying to) Learn R Markdown 
  2. Document attempts (failed or otherwise) at making TotePacking more user-friendly. 
  
## How does TotePacking work now?
It's a recursive function that takes in two vectors, item & tote dimensions, and optionally: the current count of items that fit and which iteration the function is on (not actually needed, it's a holdover from writing the function and just kind of neat to know). It returns the number of copies that fit and the count of iterations called so far.

Here's a sample of data that works with TotePacking:
```{r}
items <- read.csv("data/sample_items.csv")
head(items)
```

The main appeal of a function is being able to calculate how many copies fit, not for just one item but for MANY items. But running the function for a lot of items is a little ridiculous right now...
```{r eval = FALSE}
for (i in 1:nrow(items)){
  tempy <- TotePacking(as.vector(c(items$item_length[i], 
                                   items$item_width[i], 
                                   items$item_height[i])), 
                       as.vector(c(items$tote_length[i], 
                                   items$tote_width[i], 
                                   items$tote_height[i])))
  items$CvnQty[i] <- tempy[1]
  items$Itrs[i] <- tempy[2]
}
```

## How could TotePacking work better?
The current goal to is get to something like this...
```{r eval = FALSE}
items_fits <- TotePacking(items$item_dims,items$tote_dims)
```


Or maybe even something like this, where items is a custom data type...
```{r eval = FALSE}
items_fit <- TotePacking(items)
```

TotePacking should also be a proper *package* and not just an RStudio project. >.> 


TBC.!